RVD2: An ultra-sensitive variant detection model for low-depth targeted next-generation sequencing data

### 2013-12-13 doc/ISMB2014/RVD2.tex
Draft update.

%%%%%%%%%%%%%%%%%%%
% Appendix B: Comparison Statistics
%%%%%%%%%%%%%%%%%%%
\section{Algorithm Comparison Statistics}\label{sec:app_comparison}
Figure~\ref{fig:comparison_mcc} compares RVD2 with samtools, GATK, varscan, strelka and muTect using Matthew Correlation Coefficient (MCC)~citep(matthews1985homeostasis).

@@

\begin{figure}[ht]
\begin{center}
\includegraphics[width=140mm]{pdf_figs/comparison_table_mcc.pdf}
\caption{Matthews correlation coefficient (MCC) comparison with other variant calling algorithms.}
\label{fig:comparison_mcc}
\end{center}
\end{figure}
% from folder 'rvd2\results\2013-09-19_operating_characteristics'
% from folder 'rvd2\results\2013-09-19_operating_characteristics'

>>>>

%%%%%%%%%%%%%%%%%%%
% Appendix B: Comparison Statistics
%%%%%%%%%%%%%%%%%%%
\section{Algorithm Comparison Statistics}\label{sec:app_comparison}
Figure~\ref{fig:comparison_mcc} compares RVD2 with samtools, GATK, varscan, strelka and muTect using Matthew Correlation Coefficient (MCC)~\citep{matthews1985homeostasis}.
\begin{figure}[ht]
\begin{center}
\includegraphics[width=140mm]{pdf_figs/comparison_table_mcc.pdf}
\caption{Matthews correlation coefficient (MCC) comparison with other variant calling algorithms.}
\label{fig:comparison_mcc}
\end{center}
\end{figure}
% from folder 'rvd2\results\2013-09-19_operating_characteristics'
% from folder 'rvd2\results\2013-09-19_operating_characteristics'

@@
